The ChEMBL database as Linked Open Data

### 2012-03-29 article.tex
Added an initial LOD cloud, showing how ChEMBL-RDF embeds

>>>>

\subsection{Linked Open Data}

To make the data a proper citizen of the semantic web, we link out to various resources.
The web resources linked to as well as the predicate used for that link is given in
Figure~\ref{2}.
Links out are made to ChemSpider and RDF OpenMolecules for compounds, Bio2RDF for
protein targets, and CrossRef and Bio2RDF for DOIs and PubMed identifiers respectively.

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{figs/lodgraph}
\caption{The links out of the ChEMBL-RDF data into the Linked Open Data cloud.
Edges are labeled by the predicates making the links.}\label{2}
\end{figure}
